Milestone 2 Test: Scoring Algorithms

### 2019-10-17 perf_release_criteria/scoring_algo_analysis.Rmd
Removing manual error message.
Cleaning up text.

# tl;dr 
This is analysis to determine the feasibility of the various [scoring algorithms](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.w3huje1nj766) proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

@@

# Method
* Utilize previous saved image from proof-of-concept validation
* Compare performance metrics of Beta to Release, without any matching. On test. 
* Benchmark computation time, and memory usage (if necessary)

@@

>>> Error: cannot allocate vector of size 6.7 Gb

>>>>

# tl;dr 
This analysis determines the feasibility of the various [scoring algorithms](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.w3huje1nj766) proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee). Cramér-von Mises appears to satisfy the requirements.

@@

# Method

* Utilize previous saved image from proof-of-concept validation
* Compare performance metrics of Beta to Release, without any matching. 
* Compare performance metrics of Beta to Release, without matching.
    - Observe reduction
* Benchmark computation time, and memory usage

@@
